### 2017-03-03 Lab_4/solutions/L4-1-1.tex
Changed some previous L4 answers, added L4-5 anwers with new trace file, cleaned up L4 traces
Former-commit-id: d095ed18bcc71f5876daaae0cd962c7a5891cf27

5 broadcast beacon frame

2528 probe 
2529 probe reply
2694 association request van sta1 naar ap waar ssid in staat

>>>>

\begin{itemize}
\item Beacon frame (packet 5): broadcast by the AP (or distributed amongst stations in an IBSS network) contains the SSID, in this case, wmn-1-A.
\item Probe Request (packet 2528): the directed probe request contains the SSID of the network the station wants more information about. There are also broadcast probe requests which do not contain an SSID.
\item Probe Response (packet 2529): response from AP containing capability information, supported data rates, etc., sent after receiving a probe request. The SSID is listed under tagged parameters.
\item Association Request (packet 2694): part of the process where a station registers and connects to an AP. This first step contains the SSID with which the STA wants to connect and is sent to the corresponding AP.
\end{itemize}

### 2017-03-03 Lab_4/solutions/L4-2-1.tex
Changed some previous L4 answers, added L4-5 anwers with new trace file, cleaned up L4 traces
Former-commit-id: d095ed18bcc71f5876daaae0cd962c7a5891cf27

in de eerdere kreeg authentication als reply succesful, nu is het unspecified failure
<pkt ids>

>>>>

In the first dump, when the station sent an authentication frame (packet 2666) the AP replied with an authentication frame (packet 2668) indicating the station was succesfully authenticated (status code 0: successful).\\
In the second case, with MAC filtering enabled and configured to not allow STA1's wlan0 to connect,
the authentication frame(packet 464) sent by STA1 is met with an authentication frame(packet 466)
with status code 1. This indicates an unspecified failure. STA1 does not attempt an association as authentication failed. Note that STA1 is not informed that authentication failed because it was blacklisted. There is no reason to let a potential attacker know why exactly they could not connect.
